\section{Design Process}
\label{sec:hcimethod}
The design process was divided in 5 phases, and each phase dealt with the various key elements in a design process.

\subsection{Sense the gap}
\label{sec:sensethegap}
To sense the gap, the group studied earlier projects to get an insight in the previous solutions to the problem. The group discovered several shortcomings in the existing solution, and got an understanding of the gap in the user experience.

\subsection{Understand and refine the problem}
Further, the group defined the problems of the existing solutions and its shortcomings. The group listed some essential points of improvements, and a specification containing focus points within usability and performance was made.

\subsection{Explore}
\label{sec:explore}
Based on the information in the specification, the exploration phase started. The group members developed various suggestions for the \acrshort{gui} with specification as basis, but also took the Gestalt principles (section \ref{sec:gestaltprinciples}) and Schneidermans 8 golden rules (section \ref{sec:schneiderman}) into account.

\subsection{Evaluation and feedback}
\label{sec:evalandfeedback}
To evaluate the different suggestions, the group printed the \acrshort{gui} suggestions on sheets and arranged usability testing to get user-experienced feedback. The different screens of the interface were covered using sticky notes, but these were removed as the test person ``navigated'' through the \acrshort{gui}. The test person was given some pre-defined tasks to perform, and during the interaction he/she was not receiving any help. After performing different tasks, the person was handed an evaluation sheet, where he/she should evaluate each part of the \acrshort{gui}.

\subsection{Select plan}
\label{sec:selectplan}
This phase focuses on choosing a plan for the design, based on the result from the ``Evaluation and feedback'' phase. The group discussed the results and evaluated the suggestions based on their experience, and selected the plan to go on with.