\section{Programming the Arduino robot}
To make the whole ``Lego project'' .. NOENEO.. It is important to make the programs that run on the different robots as similar and universal as possible. The other robots are programmed in C and since the Arduino language is a set of C/C++ functions it is possible to copy the code directly and use it on the Arduino mega. It is also possible to setup a computer to directly compile and upload C code to the ATMEGA2560 chip on the Arduino. There is several steps to this, but once everything is installed and configured properly it is quick and easy to make changes or upload new programs. By doing this the same program can run on all the robots, and if there is an improvement in the code in the future, it can be installed on all robots.

\subsection{Requirements}
\textbf{AtmelStudio}

\textit{AtmelStudio 6.2} was used to edit and compile C code. AtmelStudio was chosen since most students at NTNU cybernetics is familiar with it and it is possible to configure external tools such as \textit{AVRdude} to run straight from AtmelStudio. This makes it easy to edit and upload a new programs to an Arduino. A link to the install file for \textit{AtmelStudio 6.2} is in the APPENDIX

\textbf{AVRdude}

As mentioned above, \textit{AVRdude} is used to program the Arduino board. \textit{AVRdude} is a command-line program and by passing the correct arguments it is possible to program an Arduino board. The easiest way to find the correct arguments is by showing verbose output during an upload from \textit{Arduino IDE}.

AVRdude comes with a normal \textit{Arduino IDE} installation and can be found in ``Arduino/hardware/tools/avr/bin/avrdude.exe''. It is also possible to build AVRdude from source files, but this is a much more complex process, so it is recommended to download and install \textit{Arduino IDE}

\textbf{Arduino IDE}

\textit{Arduino IDE} is the official IDE for writing and uploading code to an Arduino board. Install the latest version from www.arduino.cc.
\task{Gjøre dette om til litt mindre detaljert liste?}

\subsection{Configuring software}
There are several steps to configuring AtmelStudio to work with AVRdude and Arduino. First we need to generate the correct command-line parameters for AVRdude, then implement them into AtmelStudio. This process is explained below.

\textbf{Create command-line parameters for AVRdude}
\begin{enumerate}
    \item Start Arduino IDE and plug in your Arduino board.
    \item Press Tools -> Board, and find the correct board. In our case:
    \begin{lstlisting}
    Arduino/Genuino Mega or Mega 2560
    \end{lstlisting}
    \item Press Tools -> Processor and find the correct processor. In our case:
    \begin{lstlisting}
    ATmega2560 (Mega 2560)
    \end{lstlisting}
    \item Press Tools -> Port and set the right com port. If everything is configured properly, the board will be listed behind the COM port name.
    \item Press File -> Preferences and enable verbose on upload.
    \item Upload a minimal example project. If everything is configured properly AVRdude will print out some red text.
    \item Copy paste the last white line of text into a text editor e.g. Notepad. In our case the line is as follows:
    \begin{lstlisting}
    C:/Arduino/hardware/tools/avr/bin/avrdude -CC:/Arduino/hardware/tools/avr/etc/avrdude.conf -v -patmega2560 -cwiring -PCOM6 -b115200 -D -Uflash:w:C:/Users/teanders/AppData/Local/Temp/build219bee5ee35bdb906c90832b67c0fe23.tmp/teste.ino.hex:i
    \end{lstlisting}
    This is the arguments AtmelStudio needs to use to upload a project.
\end{enumerate}
\newpage

\textbf{Configure AtmelStudio}
\begin{enumerate}
    \item Start Atmel Studio 6.2
    \item Press File -> New -> Project -> GCC C Executable Project -> choose the correct processor, in our case:
    \begin{lstlisting}
    ATmega2560
    \end{lstlisting}
    \item Create a minimal example code, or copy paste the blinking led example in figure \ref{fig:blinkc}
    \item Press Tools -> External Tools...
    \item Change the Title: to 
    \begin{lstlisting}
    &Deploy code
    \end{lstlisting}
    \item Change Command to the first part of the text that is copied from AVRdude and then append ``.exe''. In our case:
    \begin{lstlisting}
    C:/Arduino/hardware/tools/avr/bin/avrdude.exe
    \end{lstlisting}
    \item Change arguments to ``-F '' + the parameters from the text copied from AVRdude. In our case:
    \begin{lstlisting}
    -F -v -patmega2560 -cwiring -PCOM6 -b115200 -D 
    \end{lstlisting}
    The path in Uflash needs to be a variable in order to get the correct path from AtmelStudio. To manage this, change ``-Uflash....hex'' to:
    \begin{lstlisting}
    -Uflash:w:"$(ProjectDir)Debug/$(ItemFileName).hex":i
    \end{lstlisting}
    Last add the path for AVRdude config file, in our case:
    \begin{lstlisting}
    -CC:/Arduino/hardware/tools/avr/etc/avrdude.conf
    \end{lstlisting}
    
    
    The total argument field is in our case:
    \begin{lstlisting}
    -F -v -patmega2560 -cwiring -PCOM6 -b115200 -D -Uflash:w:"$(ProjectDir)Debug/$(ItemFileName).hex":i -CC:/Arduino/hardware/tools/avr/etc/avrdude.conf
    \end{lstlisting}
    
    \item Toogle ``Use Output window'' on
    \item If everything is configured properly it is now possible to upload C code directly to the Arduino board by pressing Tools -> Deploy code
\end{enumerate}
NB! Quotes is needed before and after the file structure if the file structure contains spaces, e.g.
\begin{lstlisting}
  -C"C:/Program Files (x86)/Arduino/hardware/tools/avr/etc/avrdude.conf"
\end{lstlisting}


%%% Om de har mellomrom osv i mappenavn må man ha "" forran og etter filnavn osv.


\begin{figure}[h]
    \caption{Blinking led, C code}
    \label{fig:blinkc}
\begin{lstlisting}
/*
 * Blinking led
 *
 *  Created: 19.02.2016 10:15:22
 *  Author: teanders
 */ 

#include <avr/io.h>
#include <util/delay.h>

int main(void)
{
	DDRB = (1<<PB7);
    while(1)
    {
		PORTB = (1<<PB7);
		_delay_ms(100);
		PORTB = 0;
		_delay_ms(100);
    }
}
\end{lstlisting}
\end{figure}