\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
This master thesis ends a two-year Master's degree programme for Cybernetics and Robotics at The Norwegian University of Science and Technology, Trondheim. The thesis constitutes the basis for evaluation of the subject ``TTK4900 Teknisk Kybernetikk, Masteroppgave'', and it counts 30p for each student.

A special thanks to our supervisor and employer Tor Engebret Onshus, professor at The Department of Engineering Cybernetics. Onshus has facilitated a good dialogue throughout the project period and has laid a solid foundation for the implementation of this project.

The group would like to thank the two other cooperating parties, Erlend Ese and Eirik Thon, for great teamwork. Without our close cooperation during the project period, the resulting product would not have been as good as it became.

Further, a thank goes out to the guys at both the Cybernetics Mechanical Workshop and the Cybernetics Electronic Workshop. The Mechanical Workshop has provided us with mechanical parts, while the Electronic Workshop has provided a safe environment for building and soldering the robot, as well as electronic parts needed throughout the project period.

Finally we would like to thank the guys at office B117, for providing a social and engaging working environment.
\\[5mm]

\begin{quotation}
\color{darkred}
 \textit{``Do not seek to follow in the footsteps of others, instead, seek what they sought.''} \\
 - Matsuo Basho
\end{quotation}

\doublesignature{Mats Gjerset Rødseth}{matsroedseth@hotmail.no}{Thor Eivind Svergja Andersen}{te@svergja.com}