\chapter{Project Management}
\label{cha:projectmanagement}
Using Microsoft Project (described in Section \ref{sec:software}) as project management tool, has enabled the group to get useful insight in the project progress. Tools like MS Project is letting the user plan every part of a project in detail, which is necessary and valuable both for small and large projects (e.g. a Master Thesis).

MS Project has provided information about how the project has progressed and has made it possible to adjust the workload according to the planned progress. The adjustments provided a chance to stick with the schedule and made the group able to complete the project within the deadline. Appendix \ref{app:projman} contains Gantt diagrams from each month.

Throughout the project, the team has logged all that has been done, and this has proven to be an useful resource during the writing of the thesis. The log contains how many hours each group member has worked, and which tasks the members has been working with at the given time. The log has contributed to a general insight in what the other member has been working with. Each month the group documented their progress with a progress report, these are written in Norwegian and can be viewed in Appendix \ref{app:progressReport}.

As well as logging the work, the group held meetings with both the employer and the other teams that have been working on other parts of the system. Doing so, has enabled the teams to cooperate the best way possible, and made them able to finish the project in time. The group has logged all meetings with the employer as ``Minutes of Meeting'' and they can be viewed in Appendix \ref{app:mom}.

During the development of the software application, Git was used to ensure proper version control, and thus enabled the groups to cooperate writing code on the same application. Future projects can access a shared repository which will be updated after project end, and to prevent misunderstandings, the repository that was used during the project will not be available. This is because this project has more than 100 commits alone, and if every project were on the same repository, it would get messy  fast. The thesis was also written using version control with Git.

In addition to version control, the teams used a joint document in Microsoft OneNote to share thoughts and ideas throughout the project period. Dropbox was also used to share relevant documents.